%PDFLaTeX
\documentclass[12pt]{article}
\topmargin=-0.5cm\textwidth 16cm\textheight 22cm
\def\baselinestretch{1.4}
\oddsidemargin=-0.5cm
\pdfminorversion=4

\usepackage{color}
\usepackage{epsfig}
\usepackage{subfig}
\usepackage{mathrsfs}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{multirow}
\usepackage{amsmath,amssymb}
\usepackage{amsthm}
\usepackage{hyperref}
\usepackage{fancyhdr}
\usepackage{tabularx}
\usepackage{xfrac}
\usepackage{float}
\usepackage{amsmath}


\def\e{\epsilon}


\newtheorem{theorem}{Theorem}[section]
\newtheorem{assum}{Assumption}[section]
\newtheorem{defn}{Definition}[section]
\newtheorem{coro}{Corollary}[section]
\newtheorem{prop}{Proposition}[section]
\newtheorem{lemma}{Lemma}[section]
\newtheorem{remark}{Remark}[section]

\begin{document}

\title{Statement of Revision \\\large{Revision for ID  xxxxxxxx }\\\large{Title: ``title of the paper''}}


\maketitle

Thank you for giving us a chance to make a minor revision. We would like to thank the Editor and the Associate Editor for the kind efforts they have made for handling our manuscript. We have carefully addressed all the issues raised by the Referees, as explained in detail in our replies to their comments, and have revised the manuscript accordingly. Please kindly note that the \textcolor{blue}{blue} coloured texts are the amendments to the original paper. 

\vspace{50pt}
\underline{\textbf{\Large {Response to Reviewer 1}}}
\\

\textbf{\large{Comment 1.1:}}  \emph{the comment of the reviewer} 

\textbf{\large{Response 1.1:}}

\underline{\textbf{\Large{Revision:}}}

The original manuscript contents. \textcolor{blue}{The revised contents are colored in blue.} The original manuscript contents are here. 


\vspace{50pt}

\textbf{\large{Comment 1.2:}}  \emph{the comment of the reviewer} 

\textbf{\large{Response 1.2:}}

\vsapce{50pt}




\underline{\textbf{\Large {Response to Reviewer 2}}}
\\


\textbf{\large{Comment 2.1:}}  \emph{the comment of the reviewer}

\textbf{\large{Response 2.1:}}

\underline{\textbf{\Large{Revision:}}}

The original manuscript contents. \textcolor{blue}{The revised contents are colored in blue.} The original manuscript contents are here.



\vspace{50pt}

\textbf{\large{Comment 2.2:}}  \emph{the comment of the reviewer}

\textbf{\large{Response 2.2:}}

\vspace{50pt}


%-----------------------------------------------------------------------------------------
 



 






\end{document}
